X-Factors: External Influences of a Hockey Goaltender's Performance

### 2024-12-04 paper/paper.qmd
fixed reference tag

To analyze the effect of external factors on goaltender performance, we use a log of 394,250 shots taken during the 2021-22 to 2024-25 NHL regular and post-seasons, provided by Moneypuck [(@moneypuck)]. Moneypuck is a publicly available source of hockey analytics that tracks advanced statistics, playoff odds, and event data. The shot data is updated daily from official NHL game reports, and is organized by season. For the current 2024-25 season, data is included up to November 26, 2024.

>>>>

To analyze the effect of external factors on goaltender performance, we use a log of 394,250 shots taken during the 2021-22 to 2024-25 NHL regular and post-seasons, provided by Moneypuck [(@data)]. Moneypuck is a publicly available source of hockey analytics that tracks advanced statistics, playoff odds, and event data. The shot data is updated daily from official NHL game reports, and is organized by season. For the current 2024-25 season, data is included up to November 26, 2024.
